---
title: "Round 2: Coding Results"
editor_options: 
  chunk_output_type: console
---

This web section contains the results from the second round of coding.

Each party is listed below. You can drill into each code by starting with the ID column and clicking on a policy item. This will reveal the coders’ estimates of the party’s position. By clicking on the Coder column, you will get more detailed information from the individual coder.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r,message=FALSE,warning=FALSE}
library(here)
#library(janitor)
library(tidyverse)
library(rstatix)
library(kableExtra)
library(ggplot2)
library(ggpubr)
library(DT)
library(reactable)
library(htmltools)

```


## Alba
<details>
  <summary>Click to open data table</summary>

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data2/alba/df.rda"))
df <- df %>% rename(id=id1)
reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Source", "Justification", "Comment")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  Source = colDef(show = FALSE),
  Justification = colDef(show = FALSE),
  Comment = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```
</details> 
<br>  



## Conservatives
<details>
  <summary>Click to open data table</summary>

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data2/conservatives/df.rda"))
df <- df %>% rename(id=id1)
reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Source", "Justification", "Comment")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  Source = colDef(show = FALSE),
  Justification = colDef(show = FALSE),
  Comment = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```
</details>
<br>

## Greens
<details>
  <summary>Click to open data table</summary>

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data2/greens/df.rda"))
df <- df %>% rename(id=id1)
reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Source", "Justification", "Comment")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  Source = colDef(show = FALSE),
  Justification = colDef(show = FALSE),
  Comment = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```
</details>
<br>

## Labour
<details>
  <summary>Click to open data table</summary>

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data2/labour/df.rda"))
df <- df %>% rename(id=id1)
reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Source", "Justification", "Comment")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  Source = colDef(show = FALSE),
  Justification = colDef(show = FALSE),
  Comment = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```
</details>
<br>

## Liberal Democrats
<details>
  <summary>Click to open data table</summary>

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data2/libdems/df.rda"))
df <- df %>% rename(id=id1)
reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Source", "Justification", "Comment")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  Source = colDef(show = FALSE),
  Justification = colDef(show = FALSE),
  Comment = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```
</details>
<br>

## Plaid Cymru
<details>
  <summary>Click to open data table</summary>

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data2/plaid/df.rda"))
df <- df %>% rename(id=id1)
reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Source", "Justification", "Comment")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  Source = colDef(show = FALSE),
  Justification = colDef(show = FALSE),
  Comment = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```
</details>
<br>

## Reform
<details>
  <summary>Click to open data table</summary>

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data2/reform/df.rda"))
df <- df %>% rename(id=id1)
reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Source", "Justification", "Comment")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  Source = colDef(show = FALSE),
  Justification = colDef(show = FALSE),
  Comment = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```
</details>
<br>

## Scottish Greens
<details>
  <summary>Click to open data table</summary>

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data2/scotgreens/df.rda"))
df <- df %>% rename(id=id1)
reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Source", "Justification", "Comment")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  Source = colDef(show = FALSE),
  Justification = colDef(show = FALSE),
  Comment = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```
</details>
<br>


## SNP
<details>
  <summary>Click to open data table</summary>

```{r}
# Load the data frame (assuming df is loaded and has the described structure)

# Load drafts
load(here("data2/snp/df.rda"))
df <- df %>% rename(id=id1)
reactable(df, columns = list(
  id = colDef(name = "ID", minWidth = 250),
  coder = colDef(name = "Coder", details = function(index) {
    # Extract the sub-data for the expanded row
    sub_data <- df[index, c("Source", "Justification", "Comment")]
    # Create a mini reactable for nested display
    div(style = "padding: 16px; margin-top: -10px; margin-bottom: -10px;",
        reactable(sub_data, bordered = TRUE, compact = TRUE))
  }),
  Source = colDef(show = FALSE),
  Justification = colDef(show = FALSE),
  Comment = colDef(show = FALSE)
), defaultColDef = colDef(minWidth = 150, cell = function(value) {
  # Style for other columns
  span(style = "display: block; white-space: nowrap; overflow: hidden; text-overflow: ellipsis;", value)
}), groupBy = "id", pagination = FALSE)

```
</details>
<br>

